Fusion Moves for Correlation Clustering

### 2014-11-13 paper/egpaper_for_review.tex
update introduction/notation
update EHC
update 4.0

%%%%%%global tikz styles

@@

We stop EHC if the highest edge weight is
smaller or equal to zero  (blue edge in Fig.~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

@@

Once we know how to fuse segmentations, the actual algorithm 
for correlation clustering 
is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{Lempitsky-2010}.
We iteratively improve the best solution by
fusing it with proposal solution.
The inherent difference is how we define the fusion.
We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.

>>>>

%%%%%%global tikz styles
\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]

@@

We stop EHC if the highest edge weight is
smaller or equal to zero  (blue edge in Fig.~\ref{fig:hc_alg}). Any further edge
contraction does not improve the energies.

@@

%Once we know how to fuse segmentations, the actual algorithm 
%for correlation clustering 
%is simple and similar to the fusion move algorithm of 
As Lempitsky \etal~\cite{Lempitsky-2010}, 
we iteratively improve the best solution by
fusing it with proposal solution.
The inherent difference is how we define the fusion.
%We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
